Analysis of bulk void regions

### 2014-04-30 cosmic_voids.tex
Anlysis of the plot of FA vs Lambda_1. Tomography of the cosmic web.

The first important conclusion is regarding the distribution of the FA 
index, where there is an almost perfect correlation with the $\lambda_1$ 
eigenvalue for low values of it. This result can be interpreted as an 
one-dimensional tomography of void regions, where low $\lambda_1$ values 
are associated to the central regions of voids and they are the more 
isotropic structures found, with FA values close to 0. As we increase the 
$\lambda_1$ value, corresponding to progressively outer layers of void 
regions, the FA index increases as well, maintaining a perfect correlation 
approximately until the optimal threshold value for each scheme. Because 
of the definition of the fractional anisotropy index, it presents the 
highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$. 
Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
threshold, such that the outer regions of voids becomes highly anisotropic, 
it would imply that voids are invading filaments and sheets, so the optimal
threshold is a limit value up to which we can have void regions. For other
type of environment such as sheets, filaments and knots, the $\lambda_1$
eigenvalue does not control their spatial boundaries, so the correlation
with the FA index is no longer valid. The larger dispersion in the 
distribution indicates that contours of the FA field are no longer 
corresponding to contours of the $\lambda_1$ field. Nevertheless, for high
$\lambda_1$ values, i.e. $\lambda_1>1.0$, the median value of the FA index
decreases to lower values, indicating the presence of isotropic knots. All
of this allows us to conclude that the distribution of the FA with respect
to the $\lambda_1$ eigenvalue is not only an one-dimensional tomography of 
voids, but also an one-dimensional projection of the global structure of
the cosmic web, starting in highly isotropic central voids, passing 
through very anisotropic sheets and filaments, until isotropic knot 
regions.

>>>>

The first important conclusion is regarding the distribution of the FA 
index, where there is an almost perfect correlation with the $\lambda_1$ 
eigenvalue for low values of it. This result can be interpreted as an 
one-dimensional tomography of void regions, where low $\lambda_1$ values 
are associated to the central regions of voids and they are the more 
isotropic structures found, with FA values close to 0. As we increase the 
$\lambda_1$ value, corresponding to progressively outer layers of void 
regions, the FA index increases as well, maintaining a perfect correlation 
approximately until the optimal threshold value for each scheme. Because 
of the definition of the fractional anisotropy index, it presents the 
highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$. 
Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
threshold, such that the outer regions of voids becomes highly anisotropic, 
it would imply that voids are invading filaments and sheets, so the optimal
threshold is a limit value up to which we can have void regions. For other
type of environment such as sheets, filaments and knots, the $\lambda_1$
eigenvalue does not control their spatial boundaries, so the correlation
with the FA index is no longer valid. The larger dispersion in the 
distribution indicates that contours of the FA field are no longer 
corresponding to contours of the $\lambda_1$ field. Nevertheless, for high
$\lambda_1$ values, i.e. $\lambda_1>1.0$, the median value of the FA index
decreases to lower values, indicating the presence of isotropic knots. All
of this allows us to conclude that the distribution of the FA with respect
to the $\lambda_1$ eigenvalue is not only an one-dimensional tomography of 
voids, but also a sort of one-dimensional projection of the global 
structure of the cosmic web, starting in highly isotropic central voids, 
passing through very anisotropic sheets and filaments, until isotropic 
knot regions.
